Discriminative Sensing Based on Signal Processing for Information Security Analysis

### 2017-11-09 docs/thesis/thesis.tex
some fixes and text for tensor-dl
appendix configuration
introducion...
justificatives and problem statement
chapter 2 ok

% packages and configurations
\usepackage{enumitem}
\usepackage{lineno, hyperref}
\usepackage[numbers]{natbib}
\usepackage{babel}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{color, colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{amsthm,amsmath}
\usepackage{mathtools}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{cleveref}
\usepackage{hyperref}

@@

% Algorithmic modifications
\makeatletter
\newcommand{\ALOOP}[1]{\ALC@it\algorithmicloop\ #1%
  \begin{ALC@loop}}
\newcommand{\ENDALOOP}{\end{ALC@loop}\ALC@it\algorithmicendloop}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmicbreak}{\textbf{break}}
\newcommand{\BREAK}{\STATE \algorithmicbreak}
\makeatother

% 
\address{BRASÍLIA}

@@

\title{Discriminative Sensing Based on Signal Processing}
\date{June/2018}

\author{Thiago Pereira de Brito Vieira}
\adviser{João Paulo Carvalho Lustosa da Costa}
\coadviser{?}

@@

\include{chapters/1_introduction/introduction}
\include{chapters/2_pca_svm_cfa/pca_svm_cfa}
\include{chapters/3_eigen_similarity/eigen_similarity}
\include{chapters/4_mobile/mobile}
\include{chapters/5_tensor_dl/tensor_dl}
\include{chapters/6_conclusion_future_work/conclusion}

>>>>

% packages and configurations
\usepackage{enumitem}
\usepackage{lineno, hyperref}
\usepackage[numbers]{natbib}
\usepackage{babel}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{color, colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{amsthm,amsmath}
\usepackage{mathtools}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{cleveref}
\usepackage{hyperref}

@@

\address{BRASÍLIA}

@@

\title{Discriminative Sensing Based on Signal Processing for Information Security Analysis}
\date{November/2017}

\author{Thiago Pereira de Brito Vieira}
\adviser{João Paulo Carvalho Lustosa da Costa}
% \coadviser{?}

@@

\include{chapters/1_introduction/introduction}
\include{chapters/2_eigen_similarity/eigen_similarity}
\include{chapters/3_mobile/mobile}
\include{chapters/4_tensor_dl/tensor_dl}
\include{chapters/5_conclusion_future_work/conclusion}

\appendix
\include{chapters/appendix/a_mos/a_mos}
\include{chapters/appendix/b_pca_svm_cfa/pca_svm_cfa}
